---
title: "Color Map for R Createdy by Ibrahim Al-Hindi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Color Map for R Createdy by Ibrahim Al-Hindi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r setup}
library(Ibrrra)
library(ggplot2)
library(palmerpenguins)
```

The package `Ibrrra` is a color palette that can be used as color and fill scales with ggplot outputs. The palette contains five colors which are "red", "blue", "green", "grey", and "yellow". The scales can either be distinct or continuous.

The utilities of the package will be displayed on the `penguins` data from the `palmerpenguins` package.

We can generate a vector of colors from the color palette by specifying the number of colors using the `n` argument (maximum 5). This can be done using the `ibrrra_palette` function. The number of colors to be provided is entered inside the second set of brackets.

```{r}
ibrrra_palette()(3)
```

The order of colors outputted can be reversed by specifying `direction` = -1

```{r}
ibrrra_palette(direction = -1)(3)
```

The package provides a distinct color scale for both color and fill aesthetics in ggplot figures. The distinct color scale is implemented in the figure below

```{r}
p <- ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = species)) +
  geom_point()

p + scale_colour_ibrrra_d()
```

The order of the colors can be reversed by specifying `direction` = -1

```{r}
p + scale_colour_ibrrra_d(direction = -1)
```

The palette can also be used a distinct fill scale as below

```{r}
p <- ggplot(penguins, aes(sex, fill = species)) +
  geom_bar()

p + scale_fill_ibrrra_d()
```


Once again the order of the colors can be reversed using `direction` = -1

```{r}
p + scale_fill_ibrrra_d(direction = -1)
```


In addition to the distinct scales, `ibrrra` also provides a continuous color scale. The name of the color must be specified inside the `scale_colour_ibrrra_seq_c` function, the color must be one of "red", "blue", "green", "grey", or "yellow"

```{r}
q <- ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = flipper_length_mm)) +
  geom_point()

q + scale_colour_ibrrra_seq_c("red")
```

The degree of color lightness can be adjusted using the `amount` parameter inside the function

```{r}
q + scale_colour_ibrrra_seq_c("red", amount = 0.8)
```

The scale can also be reversed using the `direction` = -1 argument inside the function

```{r}
q + scale_colour_ibrrra_seq_c("red", amount = 0.8, direction = -1)
```










